---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753carl0026)
```

This package is a compilation of functions used throughout the semester in MATH 4753 Applied Statistical Methods.

##Functions

## myboot
Displays a confidence interval of a parameter for a given sample
```{r}
sam = dnorm(30)
a=MATH4753carl0026:::myboot2(iter=10000,sam,fun="mean",alpha=0.05)
```

## myci
Calculates a 95% confidence interval for a sample mean
```{r}
MATH4753carl0026:::myci(c(1,2,5,6))
```

## mycltp
Displays the central limit theorem for a poisson distribution
```{r}
par(mar=c(1,1,1,1))
MATH4753carl0026:::mycltp(n=10,iter=10000,lambda=2)
```

## mymaxlik
Displays the likelihood function of a parameter for a given distribution
```{r}
logbin=function(x,param){ log(dbinom(x,prob=param,size=10))}

MATH4753carl0026:::mymaxlik(x=c(3,3,4,3,4,5,5,4),param=seq(0,1,length=100),lfun=logbin,xlab=expression(p),main="Binomial",cex.main=2)
 
```
## myncurve
Returns the probability that X<a for a normal distribution
```{r}
MATH4753carl0026:::myncurve(0,1,1)
```

## runiform
Randomly generates a uniform distribution and displays it
```{r}
MATH4753carl0026:::runiform(10,100)
```
## sos
Displays sum of squares info
```{r}
fr<-lm(DAMAGE~DISTANCE,MATH4753carl0026::fire)
 MATH4753carl0026:::sumofsquares(fr, MATH4753carl0026::fire$DAMAGE)
```



